---
title: "Payne_Lab08"
author: "Deanna Payne"
date: "3/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Complete Tutorial

italics
Using _italics_ is not that hard

bold
**Bolding** words is not that hard

combine bold and italics (doesn't matter order of ** or _)
Simultaneous use of _**bolded and italicized words**_ is not that hard
Simultaneous use of **_bolded and italicized words_** is not that hard

Using # to create different sized headers
#Header 1
##Header 2
###Header 3
####Header 4
#####Header 5
######Header 6

Links (2):
1. inline link: 
[link text/description](www.link.com)

2. reference link:
Here's [a link to something else][another place].
Here's [yet another link][another-link].
And now back to [the first link][another place].

[another place]: www.github.com
[another-link]: www.google.com

Images (2): prefaced with !
1. inline image link
![alt text: phrase or sentence that describes the image for the visually impaired](www.link.com)
2. reference link
![alt text][image tag 1]
![alt text][image tag 2]

[image tag 1]: (wwww.link.com)
[image tag 2]: (www.link2.com)

Example reference link image
![The first father][First Father]

![The second first father][Second Father]

[First Father]: (http://octodex.github.com/images/founding-father.jpg)
[Second Father]: (http://octodex.github.com/images/foundingfather_v2.png)

Block Quotes
use ">" preceding text
>If you need to call special attention to a quote from another source, or design a pull quote for a magazine article, then Markdown's blockquote syntax will be useful. A blockquote is a sentence or paragraph that's been specially formatted to draw attention to the reader.

place > in front of each line of quote. useful for if quote spans multiple paragraphs (inluding breaks)
> His words seemed to have struck some deep chord in his own nature. Had he spoken
of himself, of himself as he was or wished to be? Stephen watched his face for some
moments in silence. A cold sadness was there. He had spoken of himself, of his own
loneliness which he feared.
>
> —Of whom are you speaking? Stephen asked at length.
>
> Cranly did not answer.

lists
unordered list: * to preface each item, must be on its own line
* Milk
* Eggs
* Salmon
* Butter

ordered list: numbers instead of *
1. Crack three eggs over a bowl
2. Pour a gallon of milk into the bowl
3. Rub the salmon vigorously with butter
4. Drop the salmon into the egg-milk bowl

sub bullets:indent each * one space more than preceding item
* Tintin
 * A reporter
 * Has poofy orange hair
 * Friends with the world's most awesome dog
* Haddock
 * A sea captain
 * Has a fantastic beard
 * Loves whiskey
   * Possibly also scotch?
   
bullet list with context:
paragraph must start on a line all by itself underneath the bullet point, and it must be indented by at least one space.
1. Cut the cheese
  Make sure that the cheese is cut into little triangles.

2. Slice the tomatoes
  Be careful when holding the knife.
  For more help on tomato slicing, see Thomas Jefferson's seminal essay _Tom Ate Those_.

Paragraphs
hard break
  orig: single straight line
  Do I contradict myself?
  Very well then I contradict myself,
  (I am large, I contain multitudes.)
  
  new: insert line 
  Do I contradict myself?

  Very well then I contradict myself,

  (I am large, I contain multitudes.)

soft break: insert two spaces after each new line
Do I contradict myself?··
Very well then I contradict myself,··
(I am large, I contain multitudes.)

2. Rewrite Readme
Done

3.
**Turn the logistic growth model code into a function that takes `r` (the intrinsic growth rate), `K` (the carrying capacity), and the initial population size as its arguments.**

n[t] = n[t-1] + ( r * n[t-1] * (K - n[t-1])/K )
_r ~ intrinsic growth rate_
_K ~ carrying capacity_
_population ~ initial population_
_generations ~ time or sequence of generations_

```{r}
#function
logisticGrowthModel <- function(r, K, population, generations) {
  abundance <- rep(population, length(generations))
  for (i in generations) {
    population <- population +  r * population * ((K - population)/K)
    abundance[i] <- population
  }
  plot(generations, abundance)
  myResults <- cbind(generations, abundance)
  setwd("/Users/deannagallegospayne/CompBio/CompBioLabsAndHomework/Labs/Lab08")
  write.csv(x = myResults, file = "Lab08.csv")
  return(abundance)
}
```
###arguements pulled from Payne_Lab04.R
```{r}
#try function
logisticGrowthModel(.8, 10000, 2500, seq(1:12))
```
