---
title: "Payne_Lab3.RMD"
author: "Deanna Payne"
date: "1/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Part 1: Basic Operations
```{r setup, include=FALSE}
#lab part1 step3
FlamingHotCheetos <- 5
guests <- 8
```

```{r setup, include=FALSE}
#lab part 1 step 5
guestportion <- .4
#lab part 1 step 7
hostportion <- .4
```

###Part 2: Some practice with objects that hold dta, and some practice using some built-in functions with those objects
```{r setup, include=FALSE}
self_rankings <- c(7, 6, 5, 1, 2, 3, 4)
penny_rankings <- c(5, 7, 6, 3, 1, 2,  4)
jenny_rankings <- c(4, 3, 2, 7, 6, 5, 1)
lenny_rankings <- c(1, 7, 3, 4, 6, 5, 2)
stewie_rankings <- c(6, 7, 5, 4, 3, 1, 2)
```

```{r setup, include=FALSE}
#lab part 2 step 9
PennyIV <- penny_rankings[4]
LennyIV <- lenny_rankings[4]
```

```{r setup, include=FALSE}
#lab part 2 step 10 "Concatenate"
rankingstable <- cbind(self_rankings, penny_rankings, jenny_rankings, lenny_rankings, stewie_rankings)
```

```{r setup, include=FALSE}
#lab part 2 step 11
str(PennyIV)
str(penny_rankings)
#the str(PennyIV) just depicts '3' as it is representative of Penny's numeral ranking of the 4th movie
#the str(penny_rankings) depicts the numeral vector of all the rankings Penny made for the whole Star Wars movie franchise
```

```{r setup, include=FALSE}
#pt2 step12 'For the sake of learning'
mydata <- data.frame(self_rankings, penny_rankings, jenny_rankings, lenny_rankings, stewie_rankings)
asmydata <- as.data.frame(rankingstable)
#dim# when comparing dimensions of the objects, the as.data.frame and data.fram lists the observations and variables only (7 5) indicating that there is 7 observations (a ranking) for each variable (each movie)
#str# as.data.frame and data.frame are identical, showing all the data seperated by rows of the guests and columns of the movie.
#typeof lists both as.data.frame and data.frame as a list type
```
###dim(as.data.frame)
###[1] 7 5
###str(data.frame)
###[1] 7 5


###str(as.data.frame)
###'data.frame':	7 obs. of  5 variables:
### $ self_rankings  : num  7 6 5 1 2 3 4
### $ penny_rankings : num  5 7 6 3 1 2 4
### $ jenny_rankings : num  4 3 2 7 6 5 1
### $ lenny_rankings : num  1 7 3 4 6 5 2
### $ stewie_rankings: num  6 7 5 4 3 1 2
###str(data.frame)
###'data.frame':	7 obs. of  5 variables:
### $ self_rankings  : num  7 6 5 1 2 3 4
### $ penny_rankings : num  5 7 6 3 1 2 4
### $ jenny_rankings : num  4 3 2 7 6 5 1
### $ lenny_rankings : num  1 7 3 4 6 5 2
### $ stewie_rankings: num  6 7 5 4 3 1 2


```{r setup, include=FALSE}
#step14 Episode Names
EpisodeNames <- c("I", "II", "III", "IV", "V", "VI", "VII")
rankingstable2 <- as.data.frame(rankingstable, row.names = EpisodeNames)
```


###Accessing elements of matrices and data frames

```{r setup, include=FALSE}
#third row of matrix from no.10
rankingstable[3 ,]
#fourth column from no.12
as.data.frame(rankingstable)[,4]
#access penny's ranking for episodeII
rankingstable[2,2]
#everyone's rankings for episodeII
rankingstable[2,]
#everyone's rankings for episodeII,V,VII
rankingstable[c(2, 5, 7), ]
#rankings for Penny, Jenny, and Stewie for just episodes IV and VI.
rankingstable[c(4, 6), c(2, 3, 5)]
```

```{r setup, include=FALSE}
#step 23 switch rankings Lenny II and IV
switch <- rankingstable2[2, 4]
rankingstable2[2, 4] <- rankingstable2[5, 4]
rankingstable2[5, 4] <- switch
rankingstable2
```

```{r setup, include=FALSE}
#name columns
colnames(rankingstable2) <- c("Self", "Penny", "Jenny", "Lenny", "Stewie")
rankingstable2
```

```{r setup, include=FALSE}
#step 24
#Try the example I just gave (allRankings[“III”, “Penny”]) with the matrix from step 10 and with one of the data frames from step 12 just to show yourself that it works.
rankingstable2["III", "Penny"]
asmydata <- as.data.frame(rankingstable2)
asmydata
#confirmed


##step 25 
#undoswitch from step 23
undoswitch23 <- rankingstable2["V", "Lenny"]
rankingstable2["V", "Lenny"] <- rankingstable2["II", "Lenny"]
rankingstable2["II", "Lenny"] <- undoswitch23
rankingstable2
```
###Access specifc data numbers
```{r setup, include=FALSE}
rankingstable2$Lenny
#^gives all data under Lenny
rankingstable2$Lenny[2]
#^gives second data element listed under Lenny; not "II" because is a single row unnamed (aka [1])
```

```{r setup, include=FALSE}
#redo switch from step 23
redoswitch23 <- rankingstable2$Lenny[2]
rankingstable2$Lenny[2] <- rankingstable2$Lenny[5]
rankingstable2$Lenny[5] <- redoswitch23
rankingstable2
```
